Malacology: A Programmable Storage System

### 2016-10-18 paper/paper.tex
updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

Ceph provides storage by striping and replicating data across
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such as
erasure coding, replication, and data scrubbing. Furthermore, many of these
techniques try to be autonomous so that work is distributed across the
cluster. For example, when placement groups change, the OSDs re-balance and
re-shard data in the background in a process called placement group splitting.

In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propagate changes to cluster maps throughout the
system, and autonomously initiate recovery mechanisms when failures are
discovered.

@@

The original implementation was ``hard-coded" into Ceph and lacked robustness
(no versioning, durability, or policy distribution).  Re-implemented using
Malacology, Mantle now enjoys (1) the versioning provided by the monitor
daemons and (2) the durability and distribution provided by Ceph's reliable
object store.

@@

Ensuring that the version of the current load balancer is consistent across the
physical servers in the metadata cluster was ignored in the original
implementation. The user had to set the version on each individual server and
it was trivial to make the version inconsistent.

With Malacology, Mantle stores the version of the current load balancer in the
Ceph map using the service metadata interface. The version of the load balancer
corresponds to an object name in the balancing policy. Using the service
metadata interface ensures that all metadata servers use the same version of
the load balancer. As a result, the policy version inherits the consensus and
consistency of Ceph's internal monitor daemons.

The user changes the version of the load balancer using a new CLI command:

\noindent \texttt{ fs\ set\ lua\_balancer\_class\ \textless{}version\textgreater{}}

@@

The load balancer version described above corresponds to the name of an object
in RADOS that holds the actual Lua balancing code. The objects containing load
balancer code are stored in a system-maintained group of objects (i.e. a pool).
When MDS nodes start balancing load, they first check the latest version from
the MDS map and compare it to the balancer they have loaded. If the version has
changed, they dereference the pointer to the balancer version by reading the
corresponding object in RADOS. This is in contrast to the original balancer
which stored load balancer code on the local file system -- a technique which
is unreliable and results in inconsistencies if any MDS accidently modifies the
code.

@@

In the original implementation, Mantle would log all errors, warnings, and
debug messages to the local log on each MDS. To get the simplest status
messages or to debug problems, the user would have to log into each MDS
individually, look at the logs, and reason about their causality.

With Malacology, Mantle re-usues the centralized logging features of the MON
subsystem. Important errors, warnings, and info messages are sent with the MON
beacon subsystem and appear in the monitor cluster log so instead of users
going to each node, they can watch messages appear at the monitor. Messages are
used discretly, so as not to spam the monitor with frivolous debugging but the
large events, like balancer version changes or failed subsystems show up in the
centralized log.

>>>>

Ceph provides storage by striping and replicating data across
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such as
erasure coding, replication, and data scrubbing.
Furthermore, many of these features are implemented using a peer-to-peer
protocol that allows object storage devices to operate autonomously without
a centralized coordinator.
For example, when the number of placement groups change, the OSDs re-balance and
re-shard data in the background in a process called placement group splitting
in which OSDs communicate directly with each other to coverage on a new state.
In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propagate changes to cluster maps throughout the
system, and autonomously initiate recovery mechanisms when failures are
discovered.

@@

The original implementation was ``hard-coded" into Ceph and lacked robustness
(no versioning, durability, or policy distribution).  Re-implemented using
Malacology, Mantle now enjoys (1) the versioning provided by the metadata
service interface provided by the monitor daemons and (2) the durability and
distribution provided by Ceph's reliable object store.

@@

Ensuring that the version of the current load balancer is consistent across the
physical servers in the metadata cluster was ignored in the original
implementation. The user had to set the version on each individual server and
it was trivial to make the version inconsistent. Maintaining a consistent
version is important for balancing policies that are cooperative in which
local decisions are made assuming properties about other instances of the same
policy.

With Malacology, Mantle stores the version of the current load balancer in the
Ceph service metadata interface. The version of the load balancer
corresponds to an object name in the balancing policy. Using the service
metadata interface ensures that all metadata servers use the same version of
the load balancer. As a result, the policy version inherits the
consistency of Ceph's internal monitor daemons.

The user changes the version of the load balancer using a new CLI command: \\

\noindent \texttt{\$> ceph fs\ set\ lua\_balancer\_class\ \textless{}version\textgreater{}}

@@

The load balancer version described above corresponds to the name of an object
in RADOS that holds the actual Lua balancing code.
When MDS nodes start balancing load, they first check the latest version from
the MDS map and compare it to the balancer they have loaded. If the version has
changed, they dereference the pointer to the balancer version by reading the
corresponding object in RADOS. This is in contrast to the original balancer
which stored load balancer code on the local file system -- a technique which
is unreliable and may result in silent corruption.

@@

In the original implementation, Mantle would log all errors, warnings, and
debug messages to a log stored locally on each MDS server. To get the simplest
status messages or to debug problems, the user would have to log into each MDS
individually, look at the logs, and reason about causality and ordering.

With Malacology, Mantle re-usues the centralized logging features of the
monitoring service. Important errors, warnings, and info messages are
collected
by the monitoring subsystem and appear in the monitor cluster log so instead of users
going to each node, they can watch messages appear at the monitor. Messages are
logged sparingly, so as not to spam the monitor with frivolous debugging but
important events, like balancer version changes or failed subsystems show up in the
centralized log.
